Exercise 1: Software Architecture Description of the HS07 System

### 2008-02-04 SAiP/Module1/H1/doc/paper.tex
Module View and Component and Connector updated plus small changes.

The figure shows the packages of the HS07 system, and how they interact 
with java packages used.

% ---------------------------------------------------------------------
\subsection{Component \& Connector Viewpoint}

The Component \& Connecter view consists of an Active Objects diagram and a
sequence diagram. The Active Objects diagram shows the active objects of 
the HS07 system, and how they interact.

\begin{figure}[!htb]
\center {\includegraphics[viewport=0 10 600 420,scale=0.5]{figures/cc_ao.pdf}}
\caption{HS07 Active Objects}
\label{fig:cc_ao}
\end{figure}
The sequence diagram illustrates the protocol of the interactions involved in the setup and the execution of the Gateway. It consists of a registration sequence and an infinite loop of retrieving the temperature of all registered themometers and nitifying all observers (in this case the Radiators). The example is slightly simplified to improve readability, as the registerThermometer, registerObserver, getTemperature and notify is actually network calls performed using the Invoker and the respective servers.
\begin{figure}[!htb]
\includegraphics[viewport=0 10 500 650,scale=0.3]{figures/sequence.pdf}
\caption{HS07 Sequence Diagram}
\label{fig:sequence}
\end{figure}

@@

% =====================================================================
\section{Discussion}
\subsection{Strength and Limitations of the approach}
$<<$What are the strengths and limitations of this approach to
architectural description judging from this case?$>>$

When using the approach described in \cite{christensen2004archdesc} with reverse 
engineering to achieve an architectural description, the dangers posed seem to 
be finding the correct balance in the choice of detail level. It
is easy to get to much information, cluttering the purpose of the 
AD, which in a basic sense is to clarify and present at wider understanding of
the system.

@@

The purpose of doing a reverse engineered AD must either be to evolve
the system of to extract clarification. Care should be taken to achieve either
goal. 
\subsection{Whats missing?}
$<<$Are there aspects of the software architecture that have not been
properly described?$>>$
Stakeholders and their concerns. This encompasses both users/aquirers and developers. We also need to discuss the feasibility and maintainablity of the system.

@@

$<<$For the architectural description above, discuss what (if anything) should be changed or added for it to comply with the IEEE recommended practice for architectural description$>>$

@@

\subsection{Perry \& Wolf Considerations}
$<<$Consider the definition of software architecture by [Perry and Wolf, 1992]. Discuss what the 'elements', 'form', and 'rationale' according to this definition would be for the HS07 system$>>$

@@

% =====================================================================
\section{...}

>>>>

Figure~\ref{fig:mv} shows the packages of the HS07 system, and how they interact 
with java packages used. The Sensor, Gateway and Actuator packages do not have
any knowledge of each other. They are all services that are able to respond to
HTTP queries. They uses the Invoker to interact with the other modules' HTTP
server. The interactions between the components are described in section
\ref{sec:component}. The Java packages Net, Jetty and Http are used for the
HTTP servers and HTTP requests.

% ---------------------------------------------------------------------
\subsection{Component \& Connector Viewpoint}
\label{sec:component}

The Component \& Connecter view consists of an Active Objects diagram and a
sequence diagram.

The Active Objects diagram in figure \ref{fig:cc_ao} shows the active objects
of the HS07 system, and how they interact. The Gateway accesses the thermometers
by requesting the temperature repeatedly from all registered TemperatureServices.
The measured temperature is then published to all registered observers. The
RadiatorService and ThermometerService registers to the Gateway as Observers and
Servers respectively through the GatewayService. It is also possible to register
to the Gateway from an internet connection.

\begin{figure}[!htb]
\center {\includegraphics[viewport=0 10 600 420,scale=0.5]{figures/cc_ao.pdf}}
\caption{HS07 Active Objects}
\label{fig:cc_ao}
\end{figure}
The sequence diagram illustrates the protocol of the interactions involved in the setup and the execution of the Gateway. It consists of a registration sequence and an infinite loop of retrieving the temperature of all registered themometers and nitifying all observers (in this case the Radiators). The example is slightly simplified to improve readability, as the registerThermometer, registerObserver, getTemperature and notify is actually network calls performed using the Invoker and the respective servers.
\begin{figure}[!htb]
\includegraphics[angle=90,scale=1.2]{figures/sequence.pdf}
\caption{HS07 Sequence Diagram}
\label{fig:sequence}
\end{figure}
\clearpage

@@

% =====================================================================
\section{Discussion}
\subsection{Strength and Limitations of the approach}
%$<<$What are the strengths and limitations of this approach to architectural description judging from this case?$>>$

When using the approach described in \cite{christensen2004archdesc} with reverse 
engineering to achieve an architectural description, the dangers posed seem to 
be finding the correct balance in the choice of detail level. It
is easy to get too much information, cluttering the purpose of the 
AD, which in a basic sense is to clarify and present at wider understanding of
the system.

@@

The purpose of doing a reverse engineered AD must either be to evolve
the system or to extract clarification. Care should be taken to achieve either
goal. 
\subsection{Whats missing?}
%$<<$Are there aspects of the software architecture that have not been properly described?$>>$
Stakeholders and their concerns. This encompasses both users/aquirers and developers. We also need to discuss the feasibility and maintainablity of the system.

@@

%$<<$For the architectural description above, discuss what (if anything) should be changed or added for it to comply with the IEEE recommended practice for architectural description$>>$

@@

\subsection{Perry \& Wolf Considerations}
%$<<$Consider the definition of software architecture by [Perry and Wolf, 1992]. Discuss what the 'elements', 'form', and 'rationale' according to this definition would be for the HS07 system$>>$

@@
